How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-15 tse-paper/content.tex
move listings to files to protect them from autoformat

* What went wrong:
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
Execution failed for task ':app:connectedAndroidTest'.
> com.android.builder.testing.api.DeviceException:
java.lang.RuntimeException: ...
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]

@@

\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
RegexPair,
  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true]
StartExtraction(RegexPair("Colon/$\circ$/Line Separator",
"ALL CAPS")) in EndExtraction(RegexPair("/{\color{Plum}$\varepsilon$}/",
"Line Separator/$\circ$/Line Separator"))
  \end{lstlisting}
  \caption{Simiplified regular expression produced by PBE when trained
  with examples from \Cref{lst:chunk-example}}
  \label{lst:prose-program-simplified}
\end{figure}

\lstset{
  language=,
  morekeywords={},
  texcl=false
}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
=== RUN   TestSeparator
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
--- FAIL: TestSeparator (0.03s)
    repo\_test.go:75: expected entry to be in form of `* [link] -
    description.`, got '* ...
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]
=== RUN   TestGenerateHTML
  \end{lstlisting}
  \caption{Example of a log chunk showing a linter error}
  \label{lst:chunk-example-3}
\end{figure}

@@

\lstset{
  morekeywords={INFO, WARN, 2008-11-09},
  keywordstyle=\color{Plum},
  escapeinside=**
}
\begin{figure*}[!tb]
  \centering
  \begin{lstlisting}[breaklines=true]
2008-11-09 20:46:55,556 INFO dfs.DataNode$Packet Responder: Received
block blk_3587508140 of size 67108 from /10.251.42.84
2008-11-09 20:49:46,764 WARN PacketResponder 0 for block blk\_3587508140
terminating
  \end{lstlisting}
  \caption{System Log excerpt.
Example adapted from~\cite{he2017towards}.}
  \label{lst:system-log}
\end{figure*}

>>>>

* What went wrong:
  \end{lstlisting}
  \vspace{-\baselineskip}
  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk1.txt}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]

@@

\lstset{language=caml, morekeywords={StartExtraction, RegexPosition,
RegexPair,
  EndExtraction}, keywordstyle=\bfseries\color{black}, escapeinside=//}
\begin{figure}[!t]
  \centering
  \lstinputlisting[breaklines=true]{listings/prose.txt}
  \caption{Simiplified regular expression produced by PBE when trained
  with examples from \Cref{lst:chunk-example}}
  \label{lst:prose-program-simplified}
\end{figure}

\lstset{
  language=,
  morekeywords={},
  texcl=false
}
\begin{figure}[!t]
  \centering
  \begin{lstlisting}[breaklines=true,frame=tlr]
=== RUN   TestSeparator
  \end{lstlisting}
  \vspace{-\baselineskip}
  \lstinputlisting[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]{listings/chunk2.txt}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]
=== RUN   TestGenerateHTML
  \end{lstlisting}
  \caption{Example of a log chunk showing a linter error}
  \label{lst:chunk-example-3}
\end{figure}

@@

\lstset{
  morekeywords={INFO, WARN, 2008, 11, 09},
  alsoletter=-20819,
  keywordstyle=\bfseries\color{Plum},
  escapeinside=**
}
\begin{figure*}[!tb]
  \centering
  \lstinputlisting[breaklines=true]{listings/syslog.txt}
  \caption{System Log excerpt.
Example adapted from~\cite{he2017towards}.}
  \label{lst:system-log}
\end{figure*}
